---
title: "Extract Edx Courses"
output: html_notebook
---



This dataset contains information about 976 courses that are currently available on edx.org platform. 


### Content


|variable                 |class     |description |
|:---|:---|:-----------|
|title                 |character | Title of the course|
|summary               |character | A summary of the course|
|n_enrolled             |integer | Number of student that have enrolled in the courses|
|course_type          |character | Type of course |
|institution         |character    | The institution that created and provided the course|
|instructors           |character | Name(s) of course instructors separated by '-'|
|Level         |character | Difficulty level |
|subject |character | Subject of the course |
|language            |character | Language |
|subtitles              |character | Available Subtitle(s)|
|course_effort           |character | An estimate of time and effort needed to complete the course |
|course_length        |character | length of the course in weeks|
|price           |character |  |
|course_description        |character | A description of the course|
|course_syllabus        |character | course syllabus|
|course_url        |character | course URL on edx.org|



### Acknowledgements

The dataset was scraped using R and the rvest library by Hadely Wickhom.

```{r}
library(tidyverse)
library(rvest)
library(readxl)
```

```{r}
links <-read_excel('edx_courses.xlsx')
links <- links %>% 
  filter(links !='') 
```

```{r}

extract_edx <- function(course_url) {
  Sys.sleep(5)
  html <- read_html(course_url)
  
  title <- html %>%
    html_node(xpath  = '//*[contains(concat( " ", @class, " " ), concat( " ", "mb-2", " " ))]') %>%
    html_text()
  summary <- html %>%
    html_node('#course-header p') %>%
    html_text()
  
  n_enrolled <- html %>%
    html_node('#js-number-enrolled-label .font-weight-bold') %>%
    html_text()
  
  instructors <- html %>%
    html_nodes('.name') %>%
    html_text() %>%
    paste0(collapse = '-')
  
  
  instructor_title <- html %>%
    html_nodes('.name') %>%
    html_text() %>%
    paste0(collapse = '-')
  
  instructor_org <- html %>%
    html_nodes('.name') %>%
    html_text() %>%
    paste0(collapse = '-')
  
  course_length <- html %>%
    html_nodes(
      '#main-content > div > div > div > div.col-lg-4.order-lg-2.offset-lg-1 > div > div.row.no-gutters.updated-sidebar.mb-4 > ul > li:nth-child(1) > div:nth-child(2) > span'
    ) %>%
    html_text() %>%
    paste0(collapse = '-')
  
  course_effort <- html %>%
    html_nodes(
      '#main-content > div > div > div > div.col-lg-4.order-lg-2.offset-lg-1 > div > div.row.no-gutters.updated-sidebar.mb-4 > ul > li:nth-child(2) > div:nth-child(2) > span'
    ) %>%
    html_text() %>%
    paste0(collapse = '-')
  price <- html %>%
    html_nodes(xpath = '//*[contains(concat( " ", @class, " " ), concat( " ", "m-0", " " ))]//span') %>%
    html_text() %>%
    paste0(collapse = '-')
  
  institution <- html %>%
    html_nodes(xpath = '//*[contains(concat( " ", @class, " " ), concat( " ", "partner", " " ))]//*[contains(concat( " ", @class, " " ), concat( " ", "link", " " ))]') %>%
    html_text() %>%
    paste0(collapse = '-')
  
  subject <- html %>%
    html_nodes(
      '#main-content > div > div > div > div.col-lg-4.order-lg-2.offset-lg-1 > div > div.row.no-gutters.updated-sidebar.mb-4 > ul > li:nth-child(5) > div:nth-child(2) > a'
    ) %>%
    html_text() %>%
    paste0(collapse = '-')
  
  Level <-  html %>%
    html_nodes(
      '#main-content > div > div > div > div.col-lg-4.order-lg-2.offset-lg-1 > div > div.row.no-gutters.updated-sidebar.mb-4 > ul > li:nth-child(6) > div:nth-child(2)'
    ) %>%
    html_text() %>%
    paste0(collapse = '-')
  
  language <- html %>%
    html_nodes(
      '#main-content > div > div > div > div.col-lg-4.order-lg-2.offset-lg-1 > div > div.row.no-gutters.updated-sidebar.mb-4 > ul > li:nth-child(7) > div:nth-child(2)'
    ) %>%
    html_text() %>%
    paste0(collapse = '-')
  
  subtitles <- html %>%
    html_nodes(
      '#main-content > div > div > div > div.col-lg-4.order-lg-2.offset-lg-1 > div > div.row.no-gutters.updated-sidebar.mb-4 > ul > li:nth-child(8) > div:nth-child(2)'
    ) %>%
    html_text()  %>%
    paste0(collapse = '-')
  
  course_type <- html %>%
    html_node(
      '#main-content > div > div > div > div.col-lg-4.order-lg-2.offset-lg-1 > div > div.row.no-gutters.updated-sidebar.mb-4 > ul > li:nth-child(9) > div:nth-child(2) > span'
    ) %>%
    html_text()
  
  
  course_description <- html %>%
    html_nodes('.course-description > p') %>%
    html_text()  %>%
    paste0(collapse = '')
  
  
  course_syllabus <- html %>%
    html_nodes(xpath = '//*[contains(concat( " ", @class, " " ), concat( " ", "course-description", " " ))]//div//p') %>%
    html_text()  %>%
    paste0(collapse = '')
  
  
  
  data.frame(
    course_url = course_url,
    title = title,
    summary = summary,
    n_enrolled = n_enrolled,
    course_type = course_type,
    institution = institution,
    instructors = instructors,
    instructor_org = instructor_org,
    Level = Level,
    subject = subject,
    language = language,
    subtitles = subtitles,
    course_effort = course_effort,
    course_length = course_length,
    price = price,
    course_description = course_description,
    course_syllabus = course_syllabus
  )
}


```

```{r}
safe_extract_edx <- safely(extract_edx)

edx_links <- links %>% 
  pull(links)

edx_courses <- safe_extract_edx(edx_links[1])$result
for (l in edx_links) {
  print(l)
  edx_courses <- bind_rows(edx_courses,safe_extract_edx(l)$result)
  
}


edx_courses %>% 
  write_csv('edx_courses.csv')

edx_courses %>% 
  slice(2:976) %>% 
  select(-course_url,everything(),course_url,-instructor_org) %>% 
  write_csv('edx_courses.csv')
```


